\documentclass[11pt]{article}
\setlength{\oddsidemargin}{0pt}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{listings}

\title{Predicting Popular Government, an analysis of states}

\author{Justin Hines\\
{\tt jph2149@columbia.edu}
}

\begin{document}

\maketile

\section{Abstract}

The term popularity in the modern of era takes on new meaning, especially 
considering when the exchange of information is instantaneous.  Information is
now a commodity with a viral life. The virality of 
information the internet can change public sentiment towards a variety of 
topics, products, andn issues.  In this fold has come the explotation of 
information in attempts to increase its virality. The commidification
of information by content producers has led to the expotation of said 
information, at the cost of clarity, correctness, and quality, all to attract
more end-users.  Popularity now is a means of sucess based on the merits of 
"likes", upvotes, retweets, or clicks.  \\
\\
The demand of our increasingly digital world and the instantaneous form of 
information has forced our government to enter this realm and become a content 
provider.  As such, the federal government's public image is subject to the 
virality of information. As a result, the government naturally tries to better
its public image by catering content towards its end users.  NASA is now 
popular, thanks to death, but also the virality of information spread on social
networks and the great content being pushed by NASA. \\
\\
But at what cost does this commodification occur, especially within the realm 
of government? Is it possible to garner some statisically meaning of the words 
in this content and how it relates to popularity.  If so, it would seem 
reasonable that if such a satistical trend exists, we could exploit to predict
what articles will be popular and how popular they will be.\\
\\
Thus, the goal of our modeling will be to classify articles into popularity 
levls using a Bernoulli Naive Bayes Classifer.  Such a model will be scalable
for the large dataset described below, but should also provide some insight
the word choice popularity distrubted amongst the documents, which should
prove interesting.
\section {Data}

The initial dataset for this project came from an achieved data set provided by
usa.gov in conjunction with Bit.ly.  The dataset, which can be found at 
http://bitly.measuredvoice.com/bitly_archive/?C=M;O=D and additional 
information at http://www.usa.gov/About/developer-resources/1usagov.shtml#data,
consists of a variety of data points about end-user clicks on a shorted 
governmental link.  Most governmental websites publish information through 
these links as a means of collecting analytics. The data is stored as a pub/sub
stream of JSON entries, one per line, that represent real-time clicks when the 
data is collected.  In the achieved data, the data are stored similarly.  
An entry consists of a JSON dictionary with a variety of different data points, 
including with interest to us, a bitly global hash of link, the end link, and 
the location where that click came from.\\ 
\\
The dataset includes entires from December 2011 to present day.  For the sake 
of sanity a subset of the data was used, from January 1st, 2012 to April 30th, 
2012.\\ 
\\
While this collection is certainly interesting, it provides no real insights on 
how information is being shared by what states, and what information is popular 
where, and why.  In addition, this information provides no analysis on the end 
sight beyond its link.\\
\\
In order to clean the dataset, a script was written that would filter out an 
clicks not occuring the United States (this was defined if the data entity 
contained an originating information, if that location was not in one of the 
fify United States).  In addition, in order to collect more information about 
the end site, the site at the link destination was downloaded, and filtered for
content only contained in the title or in paragraph tags.  Any sites that 
did not have over fifty words between the title and in paragraphs was 
automatically excluded.  Also, a counter was kept for each time a link was seen being 
clicked by an individual state, in addition to a global counter that kept track 
of everytime a link was clicked, regardless of the state it orginated from.\\ 
\\
In order to compute the above, since the dataset is rather large with clicks 
being on the order of mangitiate of 600k with 13k unique articles, the work
was divided and computed on an ec2 cluster, with each month being divied into 6
parts. \\
\\
In order to apply some meaning on the popularity of content (a strict threshold 
count was excluded as referring state populations differ dramaticaly), links 
were sorted by popularity in terms of click frequency, and then divided into 5
equal labels, in order from least to greatest to highest, low, medium, high, 
popular, and highly popular. The author recongizes this a rather 
naive method of applying labels, as an article in highly popular and high may 
differ by a non-statsically significant amount, but rather both lie on a 
boundary.  For sanity however, this method was applied.\\
\\
The resulting data was stored in tabular separatred value files, grouped by 
state, along with a global, with the first entry containing the global hash, location, number of 
clicks, and link content.\\ 
\\
To run the data collection and refinement system
\section{System}
For simplicity, a Bernoulli model of word occurrence in documents was used to 
generate a Naive Bayes Classification of labels, where each document is moduled 
as vector with the probablity, or weights, based on the probability of each 
word occuring in a document independently.  A Naive Bayes classifer was choosen 
for its relative cheap computation and scalabity over other models for both 
training and predictions, as training is a simple linear count of word 
frequency and prediction. Similarly, predcitions in a trained model, calculating
the logs odds is linear.\\
\\
Training and log-odds predictions were very similar to those presented in here
http://jakehofman.com/ddm/wp-content/uploads/2012/03/homework_02.pdf
For the sake of not being repeatative, I leave it to the reader to read the 
article for a further information on the classifiers.\\
\\
Performace was evaluated grouped by state on a series of different \alpha and 
\beta for smoothing.  For each state a 5x5 matrix was calculated along with 
10 most informative words for each label. Each of these runs is stored in in an output file in the log directory as 
\begin{verbatim} \log\{STATE}.log \end{verbatim}. To recap as a basic rundown of the directory structure, the final report is contained within docs/, the logs of each run of the classifier in log/ source code in src/, static requirements in requirements/ and all tsvs stored in tsv/.
\section{Analysis}
Unfortunately, the reduced dataset and filtering showed that for the majority of states, the dataset was far too sparse to properly attempt to classification.  Many states only had in the range of 100-500 unique articles, with the greatest frequency of clicks ranging from 10 to the small thousands.  In addition, the concentration of clicks was heavy in the highly popular category (while somewhat expected, many only say an increase to more than 2 articles in popular to highly popular, making attaching labels to low, medium, and high relatively irrelevant.  The only set that had enough unique articles to justify an classification and critque was the global set, and yet we have even low accuracies here. For highly popular acticles we arate of accuracy was around .239, which is fairly insigicant, with a total accruacy around .249.  For this subset the words are rather interesting, as we can see that the frequency of endorsement is high, along with aid.  The endorsement would choice could be perhaps be attributed to the recent republic primaries.  Something also of note is the lack of words about NASA, as I thought personally we would have seen a spike since the recent closure of the flight program. Appendix A includes a listing of all the 10 most informative words for each state, accuracies per label and total in adddition to the confusion matrix.

\section{Conclusion}
Overall, results were rather disappointing as I had anticpated a much densier feature space since the inital data set was so large, and seemed to infer a rich potential.  However,  the dataset was misleading in that the amount of clicks, or each line is extremely concentrated towards certain articles.  For instance, we recorded only a shy 1938 unique articles. A shy 9690 unique articles after filter with roughly only 7752 clicks in the bottom 4 labels, with the most popular article, a photo gallery http://www.whitehouse.gov/photos-and-video/photogallery/march-2012-photo-day, got 5356 clicks, which amounts to 70 percent of the entire previous four labels.  The top 15 articles amounted to 15302 clicks, roughly 50 percent of all clicks senn.  Only the top 50 articles ever saw more than 4 clicks. In short, the governemnt hasn't fallen victim to my dramatic Abstract, as no one ever vistis governemtal webistes!

\section{To Note}
The cleaning of this dataset provided to be the most difficult aspect.  On the first run through the bitly data set, I by-passed the note that I should keep a hash of articles I had seen so I don't re-download them and I only came to this realization after running the script for more than 24 hours. The second time I was running into memory issues as the amount of ram on my laptop was insufficient to store all the downloaded content.  In order to reduce space, I ran it again used c pointers using c types, but I did notice until much later than when c pointers are writen, they print the memory location the pointer as opposed to the string. It was a rather frustrating experience on my levels, and I hope you can provide some lenancy on my tardiness.  Please check my github repo at https://github.com/JustinHines/PredictingPopGov.

\section{Appendix A}

\begin{verbatium}
AL

words
['emailing', 'emanating', 'email', 'em', 'embrace', 'embedded', 'embayments', 'elk', 'emails']
words
['reported', 'healthday', 'condition', 'system', 'control', 'including', 'state', 'awareness', 'solar', 'include']
words
['fascinating', 'discover', 'professional', 'photograph', 'education', 'cosmos', 'day', 'explanation', 'apod', 'written']
words
['90', 'fascinating', 'discover', 'astronomer', 'photograph', 'featured', 'cosmos', 'explanation', 'apod', 'written']
words
['federal', 'act', 'site', 'government', 'business', 'state', 'library', 'awareness', 'requirements', 'tax']

Accuracy per Label

0.243902439024
0.285714285714
0.206896551724
0.152777777778
0.191176470588
Total Accuracy

0.252100840336


[[ 10.   8.   6.  11.  13.]
 [  8.   7.   9.  14.  10.]
 [  7.   4.   4.  19.  14.]
 [  7.   6.   5.  19.  11.]
 [  9.   3.   5.   9.  20.]]


AK


words
['content', 'life', 'address1805', 'field', 'sun', 'addthisconfig', 'blotter', 'print', 'boulder', 'google']
words
['status', 'mod', 'low', 'prediction', 'interactive', 'high', 'watch', 'issuing', '5', 'increased']
words
['night', 'easy', 'discover', 'west', 'learning', 'activities', 'park', 'quality', 'trespassing', '5']
words
['special', 'people', 'hyperlinked', 'children', 'states', 'intended', 'find', 'hyperlink', 'hyperlinks', 'united']
words
['winter', 'half', 'expanse', 'period', 'nasas', 'images', 'products', 'united', 'page', 'details']

Accuracy per Label

0.2
0.208333333333
0.0588235294118
0.3
0.285714285714
Total Accuracy

0.157142857143


[[ 1.  5.  1.  3.  4.]
 [ 2.  2.  5.  2.  3.]
 [ 0.  5.  4.  4.  1.]
 [ 1.  8.  3.  0.  2.]
 [ 1.  4.  4.  1.  4.]]


AZ


words
['employees', 'empty', 'emerging', 'employed', 'employers', 'emphysema', 'emphasized', 'employee', 'employment']
words
['science', 'research', 'res', 'make', 'institute', '17', 'diseases', 'public', 'activities', 'due']
words
['photo', 'professional', 'astronomer', 'photograph', 'fascinating', 'make', 'cosmos', 'public', 'written', 'captured']
words
['affairs', 'tools', 'test', 'social', 'message', 'systems', 'protein', 'explanation', 'end', 'called']
words
['2', 'section', 'january', 'death', 'committed', '7', 'links', 'murder', 'public', 'inmate']

Accuracy per Label

0.185714285714
0.183098591549
0.184210526316
0.25
0.19512195122
Total Accuracy

0.233727810651


[[ 13.  13.  14.  20.   8.]
 [ 11.  18.  13.  15.  11.]
 [ 16.  19.  17.  11.   5.]
 [ 19.  11.  16.  18.   4.]
 [ 11.  10.  16.  16.  13.]]


AR


words
['enhance', 'enjoy', 'enhancing', 'enlarged', 'engraver', 'engineering', 'enjoyable', 'enforcement', 'enhanced']
words
['aid', 'individuals', 'check', 'college', 'grants', 'severe', 'students', 'universities', 'grant', 'attending']
words
['visible', 'night', 'words', 'solstice', '10', '12', 'image', 'images', '2011', 'page']
words
['content', 'advisory', 'nutrition', '10', 'online', 'image', 'research', '2011', 'press', 'page']
words
['browse', 'president', 'wait', 'tour', 'sign', 'obama', 'create', 'petitions', 'video', '2012']

Accuracy per Label

0.352941176471
0.163265306122
0.125
0.217391304348
0.209302325581
Total Accuracy

0.162162162162


[[  6.   8.   2.   5.   9.]
 [  2.   7.   5.   5.  11.]
 [  3.  12.   0.   7.   8.]
 [  4.  12.   6.   2.   6.]
 [  2.  10.   3.   4.   9.]]


CA


words
['duodenum', 'duplication', 'duration', 'dunn', 'durable', 'duplex', 'dunes', 'duplicated', 'duodenojejunal']
words
['duodenum', 'duplication', 'duration', 'dunn', 'durable', 'duplex', 'dunes', 'duplicated', 'duodenojejunal']
words
['citizenship', 'market', 'economy', 'located', 'times', 'middle', '2003', 'accessible', 'schedule', 'literature']
words
['experiments', 'rehabilitation', 'items', 'opportunity', 'answers', 'society', '40', 'standards', 'district', 'brian']
words
['color', 'animal', 'official', 'corps', 'located', 'began', 'shot', 'fish', 'disk', 'inmate']

Accuracy per Label

0.197492163009
0.252032520325
0.181818181818
0.155555555556
0.178899082569
Total Accuracy

0.231741573034


[[  63.   93.   30.   21.   78.]
 [  65.   86.   36.   27.   71.]
 [  76.   80.   30.   22.   77.]
 [  66.   72.   32.   28.   87.]
 [  49.   38.   37.   37.  123.]]


CO


words
['bright', 'serum', 'continues', 'nuclear', 'clinical', 'north', '4', 'day', 'hospital', 'sciences']
words
['elaine', 'elbow', 'elderly', 'el', 'ek', 'elected', 'elder', 'election', 'elachi']
words
['act', 'degrees', 'work', 'discover', 'january', 'field', 'day', 'general', 'view', 'nasa']
words
['process', 'search', 'war', 'main', 'california', 'august', '23', 'local', 'requirements', 'year']
words
['video', 'government', 'search', 'began', 'kilometers', 'children', 'day', 'section', 'view', 'white']

Accuracy per Label

0.178571428571
0.1953125
0.102040816327
0.202380952381
0.268817204301
Total Accuracy

0.19512195122


[[ 10.  25.   5.  17.  25.]
 [ 15.  22.  11.  15.  19.]
 [ 13.  25.  10.  18.  16.]
 [  8.  33.  18.  14.   9.]
 [ 10.  23.   5.  20.  24.]]


CT


words
['effects', 'eighteen', 'ejected', 'effort', 'efficient', 'efforts', 'eighth', 'efile', 'ejection']
words
['rhode', 'increased', 'safety', 'study', 'years', 'features', 'institute', '11', 'text', 'street']
words
['hot', 'laboratory', 'technology', 'approximately', 'january', 'ground', 'institute', 'california', 'calendar', 'nasa']
words
['science', 'increased', 'order', 'office', 'safety', 'washington', 'group', 'shape', 'college', 'instructions']
words
['act', 'official', 'located', 'special', 'notices', 'identify', 'primary', 'part', 'standards', 'college']

Accuracy per Label

0.294117647059
0.231884057971
0.105263157895
0.212765957447
0.12962962963
Total Accuracy

0.258687258687


[[ 15.  16.   4.  10.   7.]
 [ 12.  15.   9.   8.   8.]
 [  6.  13.  12.   8.  13.]
 [  7.  15.   5.  12.  13.]
 [ 11.  10.   8.   9.  13.]]


DE


words
['endorse', 'end', 'ending', 'endangered', 'encourages', 'enable', 'endogenous', 'encyclopedia', 'endocannabinoid']
words
['sites', 'human', 'professional', 'information', 'group', '5', 'high', 'february', 'photograph', 'increased']
words
['med', 'medicine', 'rates', 'file', 'ncbi', 'activity', 'department', 'university', 'site', 'web']
words
['content', 'stop', 'burn', 'morning', 'recalls', 'consumers', '8', 'products', 'hazard', 'recalled']
words
['days', 'address', 'working', 'group', 'shows', 'world', 'feel', '8', 'march', 'start']

Accuracy per Label

0.0
0.25
0.166666666667
0.272727272727
0.307692307692
Total Accuracy

0.13829787234


[[ 0.  6.  3.  6.  4.]
 [ 5.  2.  2.  7.  3.]
 [ 2.  5.  6.  3.  3.]
 [ 2.  7.  6.  3.  1.]
 [ 8.  4.  1.  3.  2.]]


DC


words
['edgar', 'economy', 'ed', 'ecosystems', 'ect', 'ecosystem', 'ecuador', 'edge', 'edd']
words
['responsible', 'sun', 'division', 'usa', 'systems', 'put', 'download', 'house', '2008', 'program']
words
['support', 'representatives', 'great', 'high', 'division', '30', 'diseases', '60', 'number', 'publication']
words
['tornado', 'high', 'secretary', 'systems', 'table', 'school', '60', 'status', 'program', 'king']
words
['life', 'lifestyle', 'event', 'download', 'house', 'john', 'interactive', 'tests', 'watch', '60']

Accuracy per Label

0.178217821782
0.298850574713
0.163043478261
0.241935483871
0.157024793388
Total Accuracy

0.200863930886


[[ 18.  26.  15.  15.  19.]
 [ 20.  17.  17.  11.  28.]
 [ 28.  11.  17.   9.  28.]
 [ 17.  16.  21.  17.  22.]
 [ 18.  17.  22.  10.  24.]]


FL


words
['edsc', 'dynamics', 'edition', 'editorials', 'editions', 'editorial', 'editors', 'edison', 'edith']
words
['tornadoes', 'network', 'long', 'guide', 'moderate', 'response', 'consistent', 'events', 'table', '5']
words
['operations', 'prevalence', 'thursday', 'board', 'held', 'date', 'monday', 'ma', 'blog', 'sports']
words
['drive', 'high', 'tornadoes', 'probabilities', 'probability', 'warnings', 'mod', 'moderate', 'requirements', 'status']
words
['laboratory', 'act', 'process', 'audio', 'aid', 'short', 'northern', 'providing', '10', 'pay']

Accuracy per Label

0.246753246753
0.15625
0.211764705882
0.190476190476
0.177570093458
Total Accuracy

0.244482173175


[[ 38.  15.  18.  28.  19.]
 [ 35.  21.  11.  32.  19.]
 [ 28.  21.  22.  30.  17.]
 [ 28.  13.  20.  34.  23.]
 [ 25.  26.  14.  23.  29.]]


GA


words
['electricity', 'elections', 'electors', 'electrocution', 'elected', 'electrical', 'electrocuting', 'election', 'electric']
words
['reported', 'address', 'west', 'science', 'secretary', 'put', 'surface', '15', 'february', 'feb']
words
['working', 'resources', 'kill', 'explain', 'size', 'interest', 'clinic', 'captured', 'called', 'include']
words
['inside', 'young', 'american', 'road', 'benefits', 'interactive', 'statement', 'february', 'watch', 'visitor']
words
['summer', 'act', 'hours', 'aid', 'nation', 'county', 'programs', '11', 'maryland', 'mapcontact']

Accuracy per Label

0.170454545455
0.140845070423
0.142857142857
0.256
0.260869565217
Total Accuracy

0.184397163121


[[ 15.  10.  10.  32.  18.]
 [ 16.  16.  11.  28.  14.]
 [ 20.  15.  13.  18.  19.]
 [ 18.  20.  15.  24.   8.]
 [ 19.  10.  21.  23.  10.]]


HI


words
['enjoy', 'enter', 'enormous', 'entered', 'ensure', 'enlisted', 'engaging', 'entire', 'entities']
words
['tornadoes', 'f2f5', 'report', 'mod', 'messages', '20', 'service', 'weather', '30', 'news']
words
['fascinating', 'written', 'cosmos', 'discover', 'astronomer', 'full', '24', '20', 'photograph', 'increased']
words
['limited', 'human', 'clinicaltrialsgov', 'full', 'service', 'prices', 'purpose', 'responsibilities', 'text', 'increased']
words
['path', 'visible', 'visitor', 'receipt', 'bright', 'federal', 'kilometers', '300', 'video', 'tax']

Accuracy per Label

0.0769230769231
0.171428571429
0.272727272727
0.25
0.214285714286
Total Accuracy

0.22


[[  1.   6.   6.   4.   3.]
 [  2.  10.   3.   3.   2.]
 [  0.  10.   4.   3.   3.]
 [  6.   4.   1.   5.   4.]
 [  4.   5.   8.   1.   2.]]


ID


words
['epederuwashingtonedu', 'episodes', 'equipment', 'epigenetics', 'epimetheus', 'epidemiologist', 'equilibrium', 'epidemiology', 'equally']
words
['personal', 'trade', 'treatment', 'options', 'ftc', 'survey', 'questions', 'control', 'site', 'web']
words
['visible', 'featured', 'celebrated', 'bright', 'awareness', '7', 'dark', 'degree', 'page', 'home']
words
['nutrition', 'external', 'warning', 'file', 'find', 'management', 'click', 'javascript', 'ncbi', 'web']
words
['visible', 'cassini', 'approximately', 'solstice', 'bright', 'director', 'moon', 'dark', 'department', 'home']

Accuracy per Label

0.2
0.208333333333
0.2
0.111111111111
0.272727272727
Total Accuracy

0.173076923077


[[ 5.  5.  3.  2.  6.]
 [ 6.  7.  4.  1.  3.]
 [ 4.  5.  2.  4.  6.]
 [ 5.  5.  2.  3.  6.]
 [ 5.  2.  4.  8.  1.]]


IL


words
['earthlings', 'earners', 'earliest', 'earns', 'earned', 'earning', 'earth', 'earthshine', 'earths']
words
['impact', 'community', 'reporting', 'read', 'application', 'lung', 'institute', 'part', 'mortality', 'view']
words
['models', 'senate', 'receive', 'ca', 'order', 'market', 'committee', 'remain', 'programs', 'feet']
words
['impact', 'young', 'commitment', 'employees', 'map', 'additional', 'difference', 'campground', 'disease', 'requirements']
words
['inside', 'commitment', 'transparency', 'sign', 'union', 'house', 'create', 'executive', 'obama', 'inmate']

Accuracy per Label

0.236641221374
0.211111111111
0.21
0.14953271028
0.184713375796
Total Accuracy

0.231111111111


[[ 31.  38.  21.  16.  29.]
 [ 25.  34.  25.  21.  30.]
 [ 32.  39.  17.  19.  28.]
 [ 25.  33.  19.  31.  27.]
 [ 18.  36.  18.  20.  43.]]


IN


words
['emailing', 'elite', 'email', 'elimination', 'elk', 'ellison', 'eligibility', 'emails', 'ellipse']
words
['emailing', 'elite', 'email', 'elimination', 'elk', 'ellison', 'eligibility', 'emails', 'ellipse']
words
['time', 'presented', 'discover', 'professional', 'treatment', 'astronomer', 'featured', 'fascinating', 'written', 'universe']
words
['results', '2011', 'discover', 'death', 'business', 'based', 'fascinating', '13', '19', 'written']
words
['sci', 'indiana', 'discover', 'links', 'human', 'park', 'point', 'search', 'check', 'written']

Accuracy per Label

0.19512195122
0.269841269841
0.175438596491
0.2125
0.116279069767
Total Accuracy

0.228873239437


[[  8.  17.  10.  17.   5.]
 [ 10.  15.   8.  14.  10.]
 [  9.  13.  12.  17.   6.]
 [  5.  11.  13.  18.  10.]
 [  9.   7.  14.  14.  12.]]


IA


words
['drug', 'encyclopedia', 'endangered', 'endothelial', 'endorse', 'end', 'endorsement', 'encourages', 'ended']
words
['drug', 'encyclopedia', 'endangered', 'endothelial', 'endorse', 'end', 'endorsement', 'encourages', 'ended']
words
['int', 'details', 'approximately', 'january', 'committed', 'robert', 'students', 'school', '1', 'inmate']
words
['2011', 'atmosphere', 'ca', 'shows', 'media', 'role', 'page', 'medical', '8', 'events']
words
['browse', 'participate', 'people', 'federal', 'obama', 'video', 'comments', 'tour', 'white', 'questions']

Accuracy per Label

0.259259259259
0.153846153846
0.0967741935484
0.296296296296
0.157894736842
Total Accuracy

0.195767195767


[[  7.   6.   3.  16.   6.]
 [  4.  10.   7.   8.   9.]
 [ 10.   7.   3.  16.   2.]
 [  3.   8.   7.   8.  12.]
 [  3.   8.  11.   6.   9.]]


KS


words
['entering', 'entire', 'financing', 'entered', 'enslavement', 'enter', 'ensure', 'entitlement', 'ensign']
words
['contained', 'link', 'provided', 'application', 'products', 'privacy', '20', 'services', 'constitute', 'endorsement']
words
['fit', '2', 'discover', 'january', 'robert', 'americans', 'general', 'february', 'due', 'inmate']
words
['office', 'road', 'children', 'fall', 'public', '20', 'statement', 'environment', 'require', 'due']
words
['bright', 'act', 'small', 'life', 'office', 'human', '10', 'house', 'sun', 'apply']

Accuracy per Label

0.270833333333
0.178571428571
0.133333333333
0.111111111111
0.234042553191
Total Accuracy

0.241206030151


[[ 13.  10.   4.   2.  11.]
 [  9.  14.   5.   5.   7.]
 [  7.  12.   6.   4.  11.]
 [ 10.  11.   8.   4.   7.]
 [  9.   9.   7.   3.  11.]]


KY


words
['employ', 'emotion', 'emi', 'emotional', 'emerging', 'employer', 'employed', 'emphasizes', 'emphasized']
words
['instructed', 'illegal', 'product', 'consumers', 'safety', 'attempt', 'consumer', 'stop', 'commission', 'units']
words
['inside', 'video', 'treatment', 'safety', 'consumer', 'wait', '21', 'tax', 'version', 'inmate']
words
['summer', 'data', 'system', 'special', '10', 'house', 'interactive', 'world', 'watch', '50']
words
['browse', 'union', 'inside', 'provide', 'click', 'president', '11', 'tour', 'house', 'executive']

Accuracy per Label

0.169491525424
0.310344827586
0.142857142857
0.253731343284
0.134615384615
Total Accuracy



[[ 10.   9.   4.  17.   7.]
 [ 11.   7.   4.  11.  14.]
 [ 14.   5.   6.  12.  10.]
 [ 10.   2.   8.  18.   9.]
 [ 14.   6.   6.   9.  12.]]


LA


words
['emotion', 'enable', 'employees', 'en', 'empty', 'emphysema', 'employed', 'emphasis', 'employment']
words
['emotion', 'enable', 'employees', 'en', 'empty', 'emphysema', 'employed', 'emphasis', 'employment']
words
['drive', 'register', '2010', '2012', 'contact', 'cell', 'vehicle', 'part', '8', 'program']
words
['models', 'resources', 'great', 'office', 'developed', 'generally', 'policy', 'world', 'ncbi', 'environment']
words
['image', 'fascinating', 'discover', 'professional', 'astronomer', 'photograph', 'day', 'explanation', 'written', 'spacecraft']

Accuracy per Label

0.125
0.2
0.195652173913
0.3
0.175
Total Accuracy

0.227027027027


[[  3.   9.   9.   9.   7.]
 [  4.  11.  10.   6.   6.]
 [  4.   8.  13.   5.   7.]
 [  5.  12.   9.   3.   8.]
 [  8.   5.   5.   7.  12.]]


ME


words
['epederuwashingtonedu', 'equality', 'er', 'educating', 'equinox', 'epimetheus', 'epidermal', 'equilibrium', 'epithelial']
words
['service', 'historical', 'report', 'change', 'general', 'program', 'table', 'category', 'increased', 'weather']
words
['written', 'cosmos', 'photograph', '15', 'astronomer', 'click', 'february', 'fascinating', 'apod', 'increased']
words
['visible', 'past', 'department', '30', 'usa', 'high', 'collection', 'photographs', 'center', 'biology']
words
['president', 'people', 'sign', 'white', 'federal', 'states', 'create', 'department', 'united', 'state']

Accuracy per Label

0.190476190476
0.125
0.181818181818
0.30303030303
0.130434782609
Total Accuracy

0.288461538462


[[  4.   2.   2.  10.   3.]
 [  3.   7.   1.   6.   4.]
 [  9.   2.   2.   5.   3.]
 [  3.   2.   4.   8.   4.]
 [  2.   3.   2.   4.   9.]]


MD


words
['elevation', 'elevated', 'elements', 'eleven', 'elementary', 'elemental', 'elevator', 'eligibility', 'elevators']
words
['95', 'research', 'fire', 'email', 'title', 'heritage', 'county', 'testing', 'background', '80']
words
['address', 'documents', 'email', 'forms', 'document', 'background', '13', 'disk', 'list', 'agency']
words
['participate', 'great', 'httpwwwwhitehousegovvideo', 'discussion', 'ondemand', 'facebook', 'cell', 'northern', 'accurate', 'questions']
words
['participate', 'httpwwwwhitehousegovvideo', 'live', 'discussion', 'care', 'mission', 'ondemand', 'facebook', 'offices', 'questions']

Accuracy per Label

0.186666666667
0.176991150442
0.238938053097
0.178217821782
0.217391304348
Total Accuracy

0.245528455285


[[ 28.  20.  27.  18.  30.]
 [ 33.  29.  25.  10.  26.]
 [ 28.  22.  26.  24.  23.]
 [ 28.  26.  12.  33.  24.]
 [ 33.  16.  23.  16.  35.]]


MA


words
['enable', 'edsc', 'educ', 'edmonton', 'edmond', 'editors', 'edsitement', 'eds', 'edt']
words
['healthfindergov', 'applications', 'intended', 'office', 'guide', 'living', 'connect', 'public', 'quick', 'degree']
words
['america', 'action', 'child', 'recovery', 'office', 'share', 'point', '2009', 'navigation', '1']
words
['ca', 'angeles', 'office', 'true', 'photograph', 'living', 'general', 'consistent', 'public', 'decisions']
words
['shows', 'fit', 'easy', 'astronomer', 'featured', 'cosmos', 'explanation', 'view', 'smaller', 'degree']

Accuracy per Label

0.173913043478
0.197278911565
0.17037037037
0.220779220779
0.225490196078
Total Accuracy

0.208904109589


[[  8.  29.  23.  34.  23.]
 [  7.  28.  37.  34.  11.]
 [  9.  21.  30.  36.  21.]
 [  9.  34.  27.  28.  19.]
 [ 13.  35.  18.  22.  28.]]


MI


words
['eclipse', 'echocardiography', 'ebipubmed', 'economic', 'eatingrelated', 'ecco2', 'ecological', 'ebiomed', 'echo']
words
['reports', 'types', 'elevated', 'spectacular', 'operate', 'find', 'citizen', 'requirements', 'issues', 'articles']
words
['released', 'research', 'individuals', 'great', 'hope', 'order', 'nutrition', 'early', 'institute', 'cancer']
words
['format', 'high', 'early', 'make', '20', 'find', 'taking', 'film', 'drugs', 'planning']
words
['plan', 'preparing', 'great', 'email', 'approximately', 'notice', 'commercial', 'goals', 'make', 'andor']

Accuracy per Label

0.339285714286
0.173913043478
0.208955223881
0.149606299213
0.205882352941
Total Accuracy

0.226829268293


[[ 19.  16.  14.  19.  14.]
 [ 12.  19.  10.  28.  13.]
 [  6.  20.  17.  25.  14.]
 [ 11.  19.  15.  24.  13.]
 [  8.  18.  11.  31.  14.]]


MN


words
['el', 'eit', 'ejected', 'eib91', 'egyptians', 'effort', 'eighthgraders', 'efforts', 'efile']
words
['city', 'white', 'resources', 'great', 'secretary', 'comments', 'proclamation', 'topics', 'tour', 'tax']
words
['resources', 'research', 'involved', 'global', 'systems', 'washington', 'cancer', 'field', 'ways', 'environment']
words
['types', 'research', 'drug', 'shows', 'policy', 'protein', 'disease', 'sciences', 'multiple', 'year']
words
['applications', 'contained', 'policies', 'download', 'privacy', 'human', 'purpose', 'consistent', 'quick', 'visitors']

Accuracy per Label

0.240963855422
0.15625
0.191780821918
0.153846153846
0.223404255319
Total Accuracy

0.220963172805


[[ 20.  10.  14.   6.  21.]
 [ 17.  11.  15.   9.  19.]
 [ 19.   9.  16.  11.  16.]
 [ 15.  13.  16.  10.  17.]
 [ 12.  21.  12.   3.  21.]]


MS


words
['electricity', 'electronic', 'elevation', 'eli', 'elderly', 'einstein', 'eggs', 'elevated', 'elaine']
words
['top', 'result', 'ii', '12', 'act', 'visible', 'activity', 'continuing', 'images', 'text']
words
['practices', 'nongovernmental', 'healthy', 'link', 'states', 'services', 'purpose', 'hyperlinks', 'redirected', 'constitute']
words
['practices', 'guidance', '95', 'general', 'program', 'find', 'grant', 'grand', 'usa', 'key']
words
['path', 'contact', 'data', 'project', 'kilometers', 'questions', '300', 'sky', 'notices', 'official']

Accuracy per Label

0.166666666667
0.272727272727
0.176470588235
0.225806451613
0.235294117647
Total Accuracy

0.234375


[[  3.   3.   9.   7.   4.]
 [  7.   3.   9.   3.   4.]
 [  2.   2.  14.   5.   3.]
 [  3.   2.  13.   6.   2.]
 [  3.   1.   6.  10.   4.]]


MO


words
['current', 'address', 'data', 'condition', 'content', 'intern', 'children', '45', 'provide', '55']
words
['resources', 'community', 'stronger', 'increase', 'role', 'consumers', 'march', 'helps', 'washington', 'taxpayers']
words
['reported', 'address', 'vulnerabilities', 'northern', 'crosssite', 'attack', 'execute', 'activity', 'articles', 'agencies']
words
['time', 'past', 'medlineplus', 'system', 'approximately', 'area', 'conditions', 'february', '50', 'developed']
words
['act', 'home', 'skip', 'part', 'february', 'offices', 'follow', 'mission', 'twitter', 'today']

Accuracy per Label

0.266666666667
0.166666666667
0.194444444444
0.169491525424
0.24
Total Accuracy

0.221893491124


[[  8.  11.  21.  10.  18.]
 [  4.  17.  22.  12.  13.]
 [  6.  19.  18.  12.  13.]
 [  6.  14.  25.  12.  11.]
 [  6.   5.  22.  13.  20.]]


MT


words
['evidence', 'evol', 'events', 'execution', 'exemptions', 'excited', 'excluded', 'evolutionary', 'evident']
words
['medicine', 'approach', 'susceptible', 'external', 'warning', 'area', 'meeting', 'system', 'site', 'point']
words
['updated', 'force', 'kids', 'foods', 'news', 'people', 'health', 'guide', 'providers', 'day']
words
['pubmed', 'external', 'file', 'generate', 'javascript', 'software', 'citation', 'ncbi', 'site', 'function']
words
['pubmed', 'external', 'warning', 'file', 'generate', 'javascript', 'software', 'ncbi', 'site', 'function']

Accuracy per Label

0.0
0.125
0.285714285714
0.25
0.227272727273
Total Accuracy

0.231884057971


[[ 0.  1.  4.  4.  5.]
 [ 2.  3.  1.  3.  5.]
 [ 1.  1.  3.  3.  6.]
 [ 4.  2.  2.  5.  1.]
 [ 2.  1.  4.  1.  5.]]


NC


words
['electricity', 'electrocution', 'electro', 'electroencephalogram', 'electrode', 'electronic', 'electrodes', 'electroconvulsive', 'emails']
words
['care', 'state', 'make', 'generally', 'requirements', 'actions', 'activities', 'number', 'tax', 'taxpayers']
words
['telescope', 'pages', 'coast', 'observed', 'event', 'library', '29', '30', 'captured', '5']
words
['child', 'previous', 'healthday', 'research', 'molecular', 'institutes', '14', 'opportunities', 'due', 'made']
words
['participate', 'trauma', 'ten', 'families', 'media', 'conditions', 'facebook', 'give', 'americans', 'path']

Accuracy per Label

0.184466019417
0.232323232323
0.0925925925926
0.247787610619
0.183098591549
Total Accuracy

0.2


[[ 19.  23.   5.  28.  13.]
 [ 16.  21.  11.  25.  15.]
 [ 27.  15.  13.  19.  14.]
 [ 26.  15.  13.  20.  14.]
 [ 15.  25.  12.  21.  15.]]


NE


words
['enter', 'endorsement', 'engaged', 'endorsed', 'energy', 'engaging', 'enduran', 'engineering', 'engage']
words
['fit', 'medicine', 'earth', 'population', 'shots', 'symptoms', 'image', 'weight', 'set', 'bills']
words
['issues', 'image', 'congress', 'sex', 'march', 'department', 'drinking', 'day', 'february', 'foreclosure']
words
['visible', 'operations', '50', 'universe', 'image', 'determine', '8', '2011', 'jan', 'news']
words
['contact', 'data', 'professional', 'image', 'kilometers', 'preparing', 'locate', 'links', 'including', 'forests']

Accuracy per Label

0.181818181818
0.222222222222
0.285714285714
0.162162162162
0.130434782609
Total Accuracy

0.225806451613


[[  2.   4.  10.   6.   3.]
 [  1.   7.   7.   7.   3.]
 [  5.   2.   6.  10.   2.]
 [  1.   3.   5.   7.   9.]
 [  2.   2.   7.   7.   6.]]


NH


words
['end', 'ending', 'endorse', 'endangered', 'endorsed', 'endoftherapy', 'encyclopedia', 'endorsement', 'ended']
words
['featured', 'cosmos', 'photograph', 'professional', 'written', 'astronomer', 'fascinating', 'universe', 'explanation', 'apod']
words
['fall', 'expanding', 'level', '13', 'continue', 'department', 'hazard', 'sex', 'increased', 'washington']
words
['rate', 'special', 'learn', 'health', 'services', 'individual', 'great', 'site', 'administration', 'north']
words
['people', 'actions', 'research', 'obama', 'transparency', 'purpose', 'video', 'explain', 'watch', 'tax']

Accuracy per Label

0.263157894737
0.0526315789474
0.428571428571
0.166666666667
0.125
Total Accuracy

0.176


[[  5.   1.   9.   7.   3.]
 [  3.   2.   3.  12.   5.]
 [  4.   6.   0.  10.   5.]
 [  3.   5.   5.   8.   4.]
 [  4.   5.   4.   5.   7.]]


NV


words
['encourage', 'encountering', 'enceladus', 'encino', 'encyclopedia', 'encountered', 'encke', 'encounter', 'encouraged']
words
['contained', 'community', 'link', 'comments', 'based', 'published', '21', 'interactive', 'create', 'actions']
words
['individuals', 'live', 'space', 'low', 'facts', 'diet', 'late', '60', 'press', 'year']
words
['rover', 'science', 'shows', 'low', 'california', 'moderate', '60', 'table', '70', 'today']
words
['dollars', 'inside', 'data', 'federal', 'obama', 'astronomer', 'thunderstorm', 'notices', 'house', 'interactive']

Accuracy per Label

0.192307692308
0.222222222222
0.217391304348
0.166666666667
0.208955223881
Total Accuracy

0.240223463687


[[  5.   6.   5.   6.  14.]
 [  8.   7.   6.   3.  12.]
 [  5.   7.   3.   5.  16.]
 [  5.   3.   5.  13.  10.]
 [  3.   4.   4.   9.  15.]]


NJ


words
['educating', 'educate', 'educ', 'educational', 'educat', 'educationa', 'education', 'educationcivic', 'edge']
words
['reducing', 'west', 'business', 'red', 'office', 'secretary', 'month', 'answers', 'division', 'press']
words
['understanding', 'set', 'senate', 'shown', 'conditions', 'speaker', 'money', 'represent', 'phone', 'members']
words
['forecaster', 'tornadoes', 'network', 'rates', '3', 'moderate', 'table', '29', '30', '40']
words
['sign', 'receive', 'space', '3', '11', '4', 'section', 'requirements', '21', 'sky']

Accuracy per Label

0.23
0.179487179487
0.171875
0.258928571429
0.164705882353
Total Accuracy

0.225190839695


[[ 23.  14.  11.  29.  28.]
 [ 28.  15.   9.  23.  30.]
 [ 16.  20.  15.  21.  33.]
 [ 20.  16.  13.  21.  35.]
 [ 13.  13.  16.  18.  44.]]


NM


words
['erosion', 'equipped', 'erection', 'epimetheus', 'equity', 'essential', 'equality', 'equally', 'eric']
words
['erosion', 'equipped', 'erection', 'epimetheus', 'equity', 'essential', 'equality', 'equally', 'eric']
words
['featured', 'cosmos', 'discover', 'photograph', 'professional', 'written', 'universe', 'watch', 'fascinating', 'apod']
words
['visible', 'cassini', 'people', 'inside', 'solstice', 'suggests', 'images', 'video', 'home', 'details']
words
['browse', 'inside', 'sign', 'white', 'obama', 'interactive', 'create', 'video', 'watch', 'executive']

Accuracy per Label

0.290322580645
0.25
0.125
0.128205128205
0.263157894737
Total Accuracy

0.300751879699


[[  9.   5.   3.   5.   5.]
 [  2.   5.   9.  10.   1.]
 [  6.   3.   7.   9.   2.]
 [  7.   4.   2.  11.   3.]
 [  7.   3.   3.   4.   8.]]


NY


words
['encourage', 'aspects', 'email', 'offer', 'trade', 'disease', 'add', 'decisions', 'activities', 'feb']
words
['fema', 'records', 'congress', 'senate', 'secretary', 'assistance', 'addition', 'thomas', 'constitution', 'present']
words
['park', 'weekly', 'relationships', 'observed', 'economy', 'works', 'combination', 'position', 'turn', 'intelligence']
words
['police', 'projects', 'world', 'role', 'brightness', 'skin', 'road', 'received', 'period', 'follow']
words
['browse', 'congress', 'senate', 'higher', 'images', 'solstice', 'top', 'annual', 'cassini', 'growth']

Accuracy per Label

0.198757763975
0.17880794702
0.261194029851
0.19465648855
0.186234817814
Total Accuracy

0.20942408377


[[ 32.  27.  35.  51.  46.]
 [ 35.  29.  31.  50.  46.]
 [ 37.  34.  17.  54.  49.]
 [ 31.  33.  27.  58.  42.]
 [ 26.  28.  24.  49.  64.]]


ND


words
['experts', 'expand', 'expert', 'exercising', 'exhibition', 'examples', 'expanding', 'explanation', 'expectexplore']
words
['republic', 'copy', 'correction', 'black', 'recall', 'states', 'young', 'united', 'special', 'years']
words
['red', 'counseling', 'individuals', '12', '20', 'giant', '2012', 'based', 'mortality', 'years']
words
['updated', 'significantly', 'increase', 'information', '23', 'nasa', 'wave', 'management', '40', 'space']
words
['report', 'current', 'act', 'find', 'impact', 'files', 'high', 'including', 'sky', 'percent']

Accuracy per Label

0.428571428571
0.333333333333
0.136363636364
0.166666666667
0.166666666667
Total Accuracy

0.227272727273


[[ 3.  1.  3.  1.  1.]
 [ 1.  1.  5.  2.  0.]
 [ 2.  0.  4.  1.  2.]
 [ 1.  0.  5.  1.  2.]
 [ 0.  1.  5.  1.  1.]]


OH


words
['elevations', 'eleifend', 'elevation', 'elevated', 'elements', 'eleven', 'elementary', 'electors', 'eli']
words
['west', 'secretary', 'change', 'march', 'links', '11', '12', 'united', 'period', 'press']
words
['support', 'nuclear', 'compared', 'standard', 'global', 'committee', 'links', 'field', 'energy', 'developed']
words
['special', 'week', 'pennsylvania', '2011', 'parenting', '1', 'developed', 'pa', 'called', 'nasa']
words
['easy', 'individuals', 'links', 'page', 'human', 'making', 'picture', 'developed', 'disabled', 'programs']

Accuracy per Label

0.155555555556
0.196850393701
0.208333333333
0.198412698413
0.218045112782
Total Accuracy

0.230769230769


[[  7.  25.   5.  25.  29.]
 [  9.  27.   4.  24.  27.]
 [ 12.  28.   4.  29.  18.]
 [  8.  21.   8.  31.  23.]
 [  9.  26.   3.  17.  36.]]


OK


words
['enforecement', 'energy', 'engaged', 'enduran', 'enforce', 'endurancetrained', 'enlisted', 'enforceable', 'energysaversgov']
words
['responsible', 'asked', 'year', 'content', 'black', 'part', 'feb', 'earth', 'modifications', 'find']
words
['comments', 'professional', 'astronomer', 'links', 'photograph', 'cosmos', 'earth', 'find', 'apply', 'universe']
words
['nation', 'states', 'web', 'official', 'march', 'download', 'quality', 'page', '13', 'activity']
words
['people', 'federal', 'spacecraft', 'approximately', 'live', 'education', 'updated', 'improve', '23', 'student']

Accuracy per Label

0.473684210526
0.230769230769
0.189189189189
0.148936170213
0.2
Total Accuracy

0.247474747475


[[  9.   3.   7.  14.   7.]
 [  2.   1.  10.  18.   9.]
 [  4.   4.   4.  23.   5.]
 [  2.   3.   6.  25.   4.]
 [  2.   2.  10.  14.  10.]]


OR


words
['emanating', 'email', 'emi', 'embrace', 'embedded', 'emendationsmanuscript', 'embassy', 'emails', 'elsefrom']
words
['emanating', 'email', 'emi', 'embrace', 'embedded', 'emendationsmanuscript', 'embassy', 'emails', 'elsefrom']
words
['government', 'discover', 'january', 'pictured', 'links', 'institute', 'group', 'offers', 'apply', 'sky']
words
['effects', 'congress', 'messages', 'online', 'committee', 'library', '11', 'bill', 'earth', 'written']
words
['dark', 'order', 'discover', 'january', 'featured', 'human', 'group', 'forest', 'day', 'sky']

Accuracy per Label

0.243243243243
0.170454545455
0.2
0.25
0.191489361702
Total Accuracy

0.255395683453


[[  9.  15.  14.   9.   9.]
 [  5.  23.  10.   8.  10.]
 [  8.  12.  20.   9.   7.]
 [  8.  20.  16.   5.   7.]
 [  7.  18.  10.   5.  14.]]


PA


words
['intended', 'subject', 'contained', 'med', 'redirected', '4', '28', 'purpose', 'appearance', 'visitors']
words
['medical', 'version', 'secretary', 'product', 'accurate', 'public', 'industry', 'report', 'today', 'press']
words
['fema', 'time', 'medical', 'young', 'release', 'distant', 'save', 'recent', 'alternative', 'requirements']
words
['tornado', 'jan', 'quality', '10', 'player', 'center', '60', 'status', '70', 'made']
words
['summer', 'ut', 'act', 'medical', 'sites', 'contact', 'corps', 'create', 'psychology', 'student']

Accuracy per Label

0.170068027211
0.233009708738
0.225490196078
0.223300970874
0.172413793103
Total Accuracy

0.225


[[ 25.  24.  23.  23.  25.]
 [ 31.  29.  16.  12.  32.]
 [ 40.  13.  18.  18.  31.]
 [ 28.  22.  20.  28.  22.]
 [ 23.  15.  25.  22.  35.]]


RI


words
['employees', 'enabled', 'enacted', 'encyclopedias', 'employer', 'employee', 'employed', 'encke', 'employment']
words
['ensure', 'information', 'date', 'follow', 'opportunities', 'court', 'usa', 'day', 'privacy', 'state']
words
['updates', 'free', 'system', 'information', 'examine', 'full', 'activity', 'north', 'state', 'education']
words
['visible', 'images', 'system', 'federal', 'image', 'services', 'united', 'state', 'site', 'details']
words
['reports', 'law', 'days', 'attorney', 'data', 'general', 'health', 'received', 'sky', 'notices']

Accuracy per Label

0.25
0.2
0.2
0.357142857143
0.08
Total Accuracy

0.211382113821


[[ 6.  8.  4.  5.  2.]
 [ 6.  9.  3.  1.  6.]
 [ 6.  8.  3.  3.  5.]
 [ 5.  7.  5.  2.  6.]
 [ 1.  8.  5.  3.  6.]]


SC


words
['enjoyable', 'enjoyed', 'enhance', 'enjoying', 'enrichment', 'enhanced', 'enjoy', 'engraver', 'english']
words
['enjoyable', 'enjoyed', 'enhance', 'enjoying', 'enrichment', 'enhanced', 'enjoy', 'engraver', 'english']
words
['medlineplus', 'low', 'food', 'med', 'give', 'medical', 'written', 'events', 'moon', 'local']
words
['natural', '6', 'life', 'years', 'updates', 'important', 'fish', 'news', 'specific', 'issues']
words
['pages', 'healthday', 'caused', 'medlineplus', 'email', 'study', 'march', 'opportunity', 'island', 'news']

Accuracy per Label

0.227272727273
0.255813953488
0.217391304348
0.166666666667
0.121951219512
Total Accuracy

0.234309623431


[[ 10.  11.  15.   7.   5.]
 [  9.   7.  14.  10.   8.]
 [ 13.   8.  14.   6.   7.]
 [  6.   6.  14.  13.   9.]
 [  6.  11.  12.   6.  12.]]


SD


words
['enter', 'enhancing', 'ensure', 'engaging', 'enlarged', 'energysaversgov', 'engage', 'engineerus', 'enhanced']
words
['content', 'stop', 'discussion', 'warning', 'study', 'due', 'recent', 'area', 'society', '40']
words
['ic3', 'skip', 'charge', 'celebrated', 'living', 'fit', 'maps', 'good', 'access', 'women']
words
['hawaii', 'today', 'texas', 'edge', 'special', 'freeze', 'began', 'latest', 'dakota', '40']
words
['electronic', 'notification', 'address', 'shown', 'notifications', 'file', 'march', 'files', 'giving', 'documents']

Accuracy per Label

0.272727272727
0.0
0.2
0.5
0.206896551724
Total Accuracy

0.16


[[ 3.  0.  3.  3.  6.]
 [ 2.  2.  3.  1.  7.]
 [ 0.  5.  4.  1.  5.]
 [ 4.  1.  2.  0.  8.]
 [ 2.  6.  3.  1.  3.]]


TN


words
['edsa', 'edmundscom', 'edition', 'editions', 'editorial', 'educations', 'editors', 'edison', 'edith']
words
['rules', 'study', 'field', 'dont', 'back', 'feb', 'united', 'disease', 'text', 'samples']
words
['january', '3', 'study', 'administration', 'food', 'pages', 'response', '8', 'disease', 'lead']
words
['impact', 'provided', 'approximately', 'comments', 'control', 'human', 'phase', 'list', 'developed', 'include']
words
['power', 'november', 'official', 'photo', 'december', 'union', 'create', 'ensure', 'white', 'include']

Accuracy per Label

0.147540983607
0.288888888889
0.178947368421
0.190476190476
0.223529411765
Total Accuracy

0.207317073171


[[  9.  13.  17.   8.  19.]
 [ 16.   9.  17.   9.  15.]
 [ 13.  11.  21.   9.  12.]
 [  9.   5.  24.   9.  19.]
 [ 14.   7.  16.   7.  20.]]


TX


words
['weeks', 'diagnosis', 'active', 'total', '15', 'potential', 'part', 'environmental', 'particles', 'technology']
words
['test', 'online', 'business', 'series', 'important', 'understand', 'consistent', 'drugs', 'plan', 'called']
words
['white', 'original', 'visitor', 'flash', 'series', 'click', 'represent', 'actions', 'disk', 'suggests']
words
['white', 'obama', 'visitor', 'great', 'homeowners', 'flash', 'president', 'spent', 'engineering', 'executive']
words
['sea', 'atmosphere', 'assistance', 'generally', 'county', 'features', 'kilometers', 'mountain', 'color', 'inmate']

Accuracy per Label

0.212290502793
0.233644859813
0.184466019417
0.213709677419
0.176706827309
Total Accuracy

0.222446916077


[[ 38.  25.  38.  53.  44.]
 [ 45.  16.  48.  45.  44.]
 [ 26.  30.  39.  57.  46.]
 [ 43.  20.  43.  52.  40.]
 [ 27.  16.  38.  41.  75.]]


UT


words
['endorsed', 'endurancetrained', 'endorse', 'endangered', 'end', 'endocrinol', 'endowment', 'endorsement', 'ended']
words
['science', 'states', 'read', 'application', 'med', 'medical', 'human', 'earth', 'pm', 'united']
words
['regional', 'address', 'stress', 'details', 'special', 'hhs', 'application', 'human', 'images', 'agency']
words
['large', 'police', 'high', 'monday', 'mobile', 'center', 'direct', 'driving', '5', 'health']
words
['details', 'increase', 'kilometers', 'human', '13', '12', '4', '21', 'direct', 'health']

Accuracy per Label

0.172413793103
0.192307692308
0.289473684211
0.152173913043
0.206896551724
Total Accuracy

0.170103092784


[[  5.  10.  11.   7.   6.]
 [  5.   9.   6.  13.   6.]
 [  8.   7.   4.  15.   5.]
 [  6.  15.   7.   7.   4.]
 [  5.  11.  10.   4.   8.]]


VA


words
['electroencephalogram', 'element', 'electronic', 'electronically', 'elementary', 'ejected', 'electronics', 'elegant', 'electrodes']
words
['listed', 'west', 'complete', 'wildlife', 'filing', '3', 'make', '21', 'present', 'sky']
words
['complete', 'recent', 'pacific', 'agriculture', 'war', 'business', 'lives', 'late', 'individuals', 'meeting']
words
['online', 'november', 'links', 'make', 'transportation', 'americans', 'limited', 'diseases', 'lower', 'present']
words
['training', 'select', 'register', 'recent', 'links', 'notices', 'path', 'make', 'diseases', 'sky']

Accuracy per Label

0.212121212121
0.185185185185
0.241758241758
0.18253968254
0.192546583851
Total Accuracy

0.229773462783


[[ 28.  20.  22.  23.  31.]
 [ 33.  20.  18.  24.  29.]
 [ 20.  24.  21.  30.  29.]
 [ 26.  24.  17.  29.  28.]
 [ 25.  20.  13.  20.  44.]]


WA


words
['eclipse', 'echocardiography', 'ecliptic', 'ecologist', 'echocardiograp', 'eclipsed', 'ecological', 'echocardiogra', 'ecology']
words
['working', 'internal', 'surgical', 'network', 'support', 'county', 'point', 'supported', 'participants', 'seattle']
words
['november', 'wildlife', 'partners', 'refuge', 'locations', 'giant', 'proc', 'individual', 'complex', 'obes']
words
['foundation', 'previous', 'details', 'trust', 'located', 'january', '13', 'disk', 'design', 'united']
words
['contained', 'bright', 'register', 'internal', 'building', 'clear', 'application', 'point', 'helps', 'window']

Accuracy per Label

0.198443579767
0.199170124481
0.217573221757
0.198630136986
0.185950413223
Total Accuracy

0.223111111111


[[ 51.  48.  52.  29.  45.]
 [ 48.  52.  57.  24.  44.]
 [ 60.  61.  40.  23.  41.]
 [ 51.  44.  54.  36.  40.]
 [ 47.  36.  36.  34.  72.]]


WV


words
['epederuwashingtonedu', 'epa', 'entity', 'episodes', 'enzyme', 'epimetheus', 'ephemeral', 'environments', 'epidemiology']
words
['tornadoes', 'low', 'service', '60', 'status', '5', '70', 'category', 'table', 'increased']
words
['visible', 'images', 'current', 'shows', 'released', 'miles', '5', '1', 'attack', 'details']
words
['epederuwashingtonedu', 'epa', 'entity', 'episodes', 'enzyme', 'epimetheus', 'ephemeral', 'environments', 'epidemiology']
words
['reports', 'free', 'electronic', 'human', 'address', 'locate', 'located', 'email', 'mosaic', 'page']

Accuracy per Label

0.25
0.105263157895
0.117647058824
0.1875
0.28125
Total Accuracy

0.2


[[ 4.  2.  2.  3.  9.]
 [ 3.  5.  3.  4.  5.]
 [ 3.  6.  4.  2.  5.]
 [ 2.  4.  2.  3.  9.]
 [ 4.  2.  6.  4.  4.]]


WI


words
['encourage', 'encountering', 'enceladus', 'enclosures', 'enables', 'encke', 'encounter', 'enact', 'fenwick']
words
['small', 'increased', 'care', 'study', 'event', 'eating', 'background', 'response', '5', 'division']
words
['prediction', 'messages', 'increased', 'tornadoes', 'storm', 'mod', 'report', 'table', '5', 'category']
words
['forecaster', 'event', 'probability', 'links', '10', 'mod', 'moderate', 'table', '5', 'warnings']
words
['act', 'young', 'document', 'watershed', 'president', 'house', 'galaxy', 'school', 'watch', 'fisheries']

Accuracy per Label

0.191011235955
0.203703703704
0.238095238095
0.136363636364
0.244444444444
Total Accuracy

0.203125


[[ 17.  11.   5.   9.  22.]
 [ 17.  11.   5.  18.  13.]
 [ 12.  14.   5.  16.  17.]
 [ 27.  10.   5.   8.  14.]
 [ 16.   8.   1.  15.  24.]]


WY


words
['eventually', 'everyday', 'events', 'evening', 'event', 'evaluation', 'excited', 'evolution', 'evident']
words
['versus', 'report', 'standard', 'elevated', 'young', 'evolutionary', 'management', 'news', 'home', 'percent']
words
['vast', 'families', 'awareness', 'media', 'learn', 'health', 'purpose', '2012', 'privacy', 'bring']
words
['consistent', 'healthy', 'external', 'states', 'information', 'purpose', 'hyperlinks', 'link', 'constitute', 'appearance']
words
['remnant', 'days', 'requestedany', 'opportunity', 'representing', 'nasas', 'cygnus', 'dust', 'resolved', 'page']

Accuracy per Label

0.0
0.0
0.333333333333
0.307692307692
1.0
Total Accuracy

0.105263157895


[[ 0.  0.  2.  4.  2.]
 [ 1.  1.  1.  5.  0.]
 [ 5.  2.  1.  0.  0.]
 [ 3.  2.  1.  2.  0.]
 [ 2.  1.  1.  2.  0.]]


global


words
['lives', 'winds', 'agents', 'cloud', 'question', 'saving', 'feel', 'associations', 'ago', 'deaths']
words
['diverse', 'divemaster', 'diverging', 'diver', 'divalent', 'divergent', 'div', 'diverselandscape', 'divers']
words
['hyperlinks', 'presidential', 'rules', 'consistent', 'tip', 'stress', 'leg', 'potentially', 'appearance', 'regulation']
words
['integrity', 'lewis', 'put', 'maine', 'rules', 'properly', 'suite', 'successfully', 'easy', 'potentially']
words
['constitute', 'hyperlinks', 'hyperlink', 'aid', 'shot', 'quick', 'healthfindergov', 'hyperlinked', 'appearance', 'endorsement']

Accuracy per Label

0.225352112676
0.236593059937
0.175438596491
0.242924528302
0.168601716305
Total Accuracy

0.250360899154

[[ 208.  225.  100.  103.  334.]
 [ 200.  209.  128.   81.  352.]
 [ 191.  216.  130.   99.  334.]
 [ 176.  195.  121.   92.  386.]
 [ 148.  106.   91.   49.  575.]]
 \end{verbatim}
 \end{document}
